### 2023-03-08 manuscript.tex
Fixing captions [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6f7126e88d2a25b0e683001ae1a3f9a04bfc43e1.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6f7126e88d2a25b0e683001ae1a3f9a04bfc43e1/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4367467250

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/454ea98fc5bad08fda4ba675c377a7db51d7a419/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/454ea98fc5bad08fda4ba675c377a7db51d7a419}{SORTEE-Github-Hackathon/manuscript@454ea98}
on March 8, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-HtStoSAI}{}}%
Sabatini, F. M., Lenoir, J., Hattab, T., Arnst, E. A., Chytrý, M., Dengler, J., De Ruffray, P., Hennekens, S. M., Jandt, U., Jansen, F., Jiménez-Alfaro, B., Kattge, J., Levesley, A., Pillar, V. D., Purschke, O., Sandel, B., Sultana, F., Aavik, T., Aćić, S., \ldots{} Bruelheide, H. (2021). sPlotOpen -- an environmentally balanced, open-access, global dataset of vegetation plots. \emph{Global Ecology and Biogeography}, \emph{30}(9), 1740--1764. https://doi.org/\url{https://doi-org.lib-ezproxy.concordia.ca/10.1111/geb.13346}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6f7126e88d2a25b0e683001ae1a3f9a04bfc43e1/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6f7126e88d2a25b0e683001ae1a3f9a04bfc43e1}{SORTEE-Github-Hackathon/manuscript@6f7126e}
on March 8, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-HtStoSAI}{}}%
Sabatini, F. M., Lenoir, J., Hattab, T., Arnst, E. A., Chytrý, M., Dengler, J., De Ruffray, P., Hennekens, S. M., Jandt, U., Jansen, F., Jiménez-Alfaro, B., Kattge, J., Levesley, A., Pillar, V. D., Purschke, O., Sandel, B., Sultana, F., Aavik, T., Aćić, S., \ldots{} Bruelheide, H. (2021). sPlotOpen -- an environmentally balanced, open-access, global dataset of vegetation plots. \emph{Global Ecology and Biogeography}, \emph{30}(9), 1740--1764. \url{https://doi.org/10.1111/geb.13346}
